### 2019-08-07 thesis.tex
*** empty log message ***

Astrophysical plasmas\footnote{In the literature, the term ``astrophysical
  plasma'' is sometimes used to refer to the plasma observed outside the solar
  system, while ``space plasma'' is used to account for the plasma in our
  interplanetary space. In this text, however, both terms are being used as
  synonyms.} are observed in a vast range of densities, temperatures, magnetic
fields, ionization degree, and scale lengths\footnote{A comprehensive
  description of the scales and characteristics of cosmic plasmas can be seen
  in Section 1.2 of Ref. \cite{peratt2014}.}. Starting in the outer layers of
Earth's atmosphere, passing through the solar wind in the interplanetary space,
to the stellar interiors and atmospheres, accretion disks, and molecular clouds
it is estimated that something around $99 \sim 99.9\%$ of the observable matter
in the universe is in the plasma state. Under cosmic conditions, even the weakly
ionized gas of the neutral hydrogen regions around galaxies or in the atmosphere
of cold stars have a strong reaction to electromagnetic fields, exhibiting the
characteristic collective behavior of plasmas and, therefore, are also considered
plasmas\cite{tsypa,may,peratt2014}.

@@

The analysis presented in this doctoral thesis was analyzed in the context
of solar physics. 
% In this appendix we present a brief discussion on the current state-of-art
% solar physics and

\section{Solar and space physics}
\label{sec:solar-physics}
Solar physics can be thought of as a combination of plasma and space physics.
The wide variety of plasmas and the accessibility to direct, in situ measurements,
highly resolved remote sensing and high-resolution spectroscopy turned the solar
system into Earth's plasma physics laboratory in space.
%% falar sobre como física sola pode contribuir para fśica de plasmas em geral

The solar system is permeated with a constant plasma flow of solar origin.
This tenuous and rapid flowing plasma, know as \emph{solar wind}, is
expelled

% The Sun is a G2 main-sequence star. From the stellar astrophysics point
% of view, it is considered ordinary, without any unique property that could
% differentiate it from other main-sequence stars; except for the fact that
% it is remarkably close to us. These two facts make the Sun a perfect model
% of study not only for several areas of astrophysics, like stellar structure
% and evolution, but also for plasma physics.

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.48\textwidth]{corona2017.png}
    \includegraphics[width=0.4305\textwidth]{high-contrast-corona.png}
    \caption{Solar corona captured during the total solar eclipse of 2017.
      {\footnotesize Credit:}
      \href{https://hdr-astrophotography.com/high-resolution-2017-total-solar-eclipse/}
      {\footnotesize Nicolas Lefaudeux}{\footnotesize , accessed at 05/06/2019}.}
    \label{figD1}
  \end{center}
\end{figure}

% The theory developed during this graduate research makes use of solar physics
% results to contribute on both sides. In \cite{Tigik2016a},
% \cite{Tigik2016b} and \cite{Tigik2017b}, we present theoretical and
% numerical evidence of plasma processes that might aid in the interpretation
% and accurate modeling  of phenomena observed in the solar plasma. While in
% \cite{Tigik2017a}, we introduce a new equation depicting an unknown process
% and numerically analyze it in the context of solar physics; its existence
% outside theory, however, will depend on the development of more advanced
% space probes to be confirmed.

>>>>

% \footnote{In the literature, the term ``astrophysical
%   plasma'' is sometimes used to refer to the plasma observed outside the solar
%   system, while ``space plasma'' is used to account for the plasma in our
%   interplanetary space. In this text, however, both terms are being used as
%   synonyms.}

% \footnote{A comprehensive description of the scales and characteristics of
%   cosmic plasmas can be seen in Section 1.2 of Ref. \cite{peratt2014}.}

Astrophysical plasmas are observed in a vast range of densities, temperatures,
magnetic fields, ionization degree, and scale lengths\cite{peratt2014}. Starting
in the outer layers of Earth's atmosphere, passing through the solar wind in the
interplanetary space, to the stellar interiors and atmospheres, accretion disks,
and molecular clouds it is estimated that something around $99 \sim 99.9\%$ of the
observable matter in the universe is in the plasma state. Under cosmic conditions,
even the weakly ionized gas of the neutral hydrogen regions around galaxies or in
the atmosphere of cold stars have a strong reaction to electromagnetic fields,
exhibiting the characteristic collective behavior of plasmas and, therefore, are
also considered plasmas\cite{tsypa,may,peratt2014}.

@@

The theory developed during this graduate research analyses the combined
action of nonlinear kinetic instabilities and collisional processes in
the context of solar physics. To contextualize our work within the solar
plasma research, in this appendix, we present a brief review of the
current state-of-art of solar physics, followed by a discussion on the
plasma phenomena related to our study.

\section{Solar and space physics}
\label{sec:solar-physics}
The solar system is permeated with a constant plasma flow of solar origin.
This tenuous and rapid flowing plasma is the solar wind. It enfolds the Earth
as it travels outward the solar system, creating a region around the Sun that
extends to approximately $140\unit{AU}$ in the surrounding galactic space.
This region, called heliosphere, is the domain of solar and space physics. In
the boundaries of the heliosphere, the outward pressure of the solar plasma
balances the inward pressure from the interstellar medium. This interface
region, the heliopause, limits the volume in the galactic environment that is
under the influence of the solar wind \cite{NAP13060}. A general depiction of
the heliosphere and its main boundaries is depicted in \autoref{figD1}, where
the termination shock separates the inner and outer regions of the heliosphere.

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.48\textwidth]{Heliosphere_main_Boundaries}
    \caption{Main boundaries of the heliosphere.
      {\footnotesize Credit:}
      \href{https://science.nasa.gov/heliophysics/focus-areas/heliosphere}
      {\footnotesize NASA}{\footnotesize , accessed at 07/08/2019}.}
    \label{figD1}
  \end{center}
\end{figure}

Solar physics can be thought of as a combination of plasma and space physics.

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.48\textwidth]{corona2017.png}
    \includegraphics[width=0.4305\textwidth]{high-contrast-corona.png}
    \caption{Solar corona captured during the total solar eclipse of 2017.
      {\footnotesize Credit:}
      \href{https://hdr-astrophotography.com/high-resolution-2017-total-solar-eclipse/}
      {\footnotesize Nicolas Lefaudeux}{\footnotesize , accessed at 05/06/2019}.}
    \label{figD2}
  \end{center}
\end{figure}
